---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.com/obrl-soil/slga.svg?branch=master)](https://travis-ci.com/obrl-soil/slga)
[![Coverage status](https://codecov.io/gh/obrl-soil/slga/branch/master/graph/badge.svg)](https://codecov.io/github/obrl-soil/slga?branch=master)

# slga

slga offers the ability to download geographic subsets of raster data from the [Soil and Landscape Grid of Australia](www.clw.csiro.au/aclep/soilandlandscapegrid/). The Grid was generated in 2014 from a compilation of Australian soil and landscape data and contains a set of modelled soil attributes that meet the [globalsoilmap.net](http://globalsoilmap.net/) specification. 

Also available for download are a set of terrain and climate covariates considered useful in soils modelling. These are primarily derived from [GeoScience Australia's](http://www.ga.gov.au/) [SRTM DEM products](http://www.ga.gov.au/scientific-topics/national-location-information/digital-elevation-data).

All products are returned in GDA94 long/lat (EPSG:4283) and have a cell resolution of 3" (roughly 90m). 

## Installation

Install from github with

```{r 'installation', eval = FALSE}
devtools::install_github("obrl-soil/slga")
```

## How it works

`slga` uses the WCS endpoints provided by the SLGA to access data. The package endeavours to return requested products as simple subsets of the parent dataset, with no hidden server-side resampling.

## Example

```{r pkgs}
library(raster)
library(slga)
```

```{r demo, eval = FALSE}
# get surface clay content for King Island
aoi <- c(143.75, -40.17, 144.18, -39.57)
ki_surface_clay <- get_slga_data(product = 'TAS', attribute = 'CLY',
                                 component = 'all', depth = 1,
                                 aoi = aoi, write_out = FALSE)
```

```{r dplot, echo = FALSE, results = 'hold'}
data('ki_surface_clay')
plot(ki_surface_clay, zlim = c(0, 65), nc = 3)
```

See the package vignette for further detail.

### Warning!

While it is possible to download data for large extents using this package, please be aware that the data volume can get large, and it will not be very quick or efficient. If you want to obtain SLGA data for a significant proportion of Australia, you may prefer to access the full datasets via the [CSIRO Data Access Portal](https://data.csiro.au/dap/home?execution=e1s1). Note that 1" (30m) versions of the slga terrain attributes are also available on that portal.

### Asking for help

If you get stuck using this package or the data it provides, please post a question on [Stack Overflow](https://stackoverflow.com/) (for internet connectivity problems) or the [GIS StackExchange](https://gis.stackexchange.com/) (for raster/geospatial issues). This means that others can benefit from the discussion, and more people are available to help you. You're welcome to ping me in a comment on those websites or on twitter (@obrl_soil) to get my attention.

*** 
